\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-05 NAR_DRAFT.tex
minor change
grammar

\batcave is a post-call variant evalutation tool that uses MuTect output and the tumor-specific mutation profile to sharpen the posterior probability assigned to SNVs.
We demonstrated here that \batcave improves classification accuracy in synthetic data, leading to better more accurate variant calls at any posterior probability threshold.
Importantly, \batcave is better calibrated than MuTect at relevant probability thresholds, allowing researchers and clinicians to make informed choices about the trade-off between precision and recall.
We are unable to study calibration in real data, because complete false positive/true negative data is not available in currently available for real data
Deep sequencing experiments where a large random sample of uncalled potential variants, as well as a random sample of variant with no reads at all present, would give much-needed insight into the differences in statistical models in variant calling.

@@

We hope that the availability of this algorithm will have a positive effect on the cost/benefit ratio of deeper sequencing in both research and clinical applications.
One size does not fit all with respect to the evidence threshold. 
Users are interested in true and false positive fractions, and users of different types will have different trade-offs in terms of precision and recall.
\batcave is designed to present the user with a more accurate sense of these trade-offs.

>>>>

\batcave is a post-call variant evalutation tool that uses MuTect output and the tumor-specific mutation profile to sharpen the posterior probability assigned to SNVs.
We demonstrated here that \batcave improves classification accuracy in synthetic data, leading to better more accurate variant calls at any posterior probability threshold.
Importantly, \batcave is better calibrated than MuTect at relevant probability thresholds, allowing researchers and clinicians to make informed choices about the trade-off between precision and recall.
We are unable to study calibration in real data, because complete false positive/true negative data for real data is not available. 
Deep sequencing experiments where a large random sample of uncalled potential variants, as well as a random sample of variant with no reads at all present, would give much-needed insight into the differences in statistical models in variant calling.

@@

We hope that the availability of this algorithm will have a positive effect on the cost/benefit ratio of deeper sequencing in both research and clinical applications.
One size does not fit all with respect to the evidence threshold. 
Users are interested in true and false positive fractions, and users of different types will have different trade-offs in terms of precision and recall.
We present \batcave, and the R package \texttt{batcaver} to provide the user with a more accurate sense of these trade-offs.
